Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\mathbf{\sqrt{s_\mathrm{NN}} = 2.76}$~TeV

### 2016-11-08 paper.tex
final ante's comment in place

\begin{document}%

\linenumbers

@@

The correlations between event-by-event fluctuations of amplitudes of anisotropic flow harmonics
in $\PbPb$ collisions at $\snn=2.76$~TeV have been measured with the ALICE detector at the Large Hadron Collider. 
The results were obtained with the new multi-particle cumulant method dubbed symmetric cumulants.
This method is robust against systematic biases originating from non-flow effects. 
The centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations are presented. 
The results are compared to calculations from viscous hydrodynamics and  A Multi-Phase Transport ({AMPT}) models.
The comparisons to viscous hydrodynamic models demonstrate that
the different order Fourier harmonic correlations respond differently to the initial conditions or the shear viscosity to the entropy density ratio ($\eta/s$). The small $\eta/s$ regardless of initial conditions is favored and the small $\eta/s$ with the AMPT initial condition is closest to the results. 
$v_3$-$v_2$ and $v_4$-$v_2$ correlations show moderate $p_{\rm T}$ dependence in mid central collisions. This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out, which might help to understand bulk viscosity in hadronic phase.
% which is the least understood part of hydrodynamic calculations.
%However the $v_3$-$v_2$ and  $v_4$-$v_3$ cannot be described by any model setting.
%pt dependence ??
Together with the existing measurements of individual flow harmonics the presented results provide further constraints 
on initial conditions and the transport properties of the system produced in heavy-ion collisions.
\end{abstract}
\end{titlepage}
\setcounter{page}{2}

@@

\begin{figure}[htbp]
            \begin{center}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
        \caption{The result of SC$(m,n)$ (left figure) and NSC$(m,n)$ (right figure) with flow harmonic order up to $5^{\mathrm{th}}$ in $\PbPb$ collisions at $\snn=2.76$~TeV. Note that the lower order harmonic correlations are taken from the recent publication~\cite{ALICE:2016kpq} and only statistical errors are shown for both figures. SC(4,2) and SC(3,2) are scaled down by factor of 10 on the left.}
        \label{fig:Figure_1}
              \end{center}
\end{figure}

@@

\section{Model Comparisons}
\label{sec:theory}
\subsection{Low Order Harmonic Correlations}
SC(3,2) and SC(4,2) are compared to several theoretical calculations. 
First, the fluid hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy ratio $\eta/s(T)$ are shown on the in Fig2 in Ref.~\cite{ALICE:2016kpq}. 
It has been demonstrated that NSC(3,2) observable is sensitive mainly to the initial conditions, while NSC(4,2) observable is sensitive to both the initial conditions and the system properties, which is consistent with the prediction from~\cite{Niemi:2012aj}.
However, the sign of NSC(3,2) is positive in the models in 0-10\% central collisions while it is negative in data.
In the most central collisions the anisotropies originate mainly from fluctuations, i.e.\ the initial ellipsoidal geometry characteristic for mid-central collisions plays little role in this regime. Hence this observation will help to understand the fluctuations in initial conditions better.
NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations, i.e.\ medium property but the model cannot describe the centrality dependence nor the absolute values. These observed distinct discrepancies between data and models might indicate that the current understanding of initial conditions used in the model need to be revisited to further constrain the $\eta/s(T)$, considering the difficulties on separating the role of the $\eta/s$  from the initial condition to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
Hence the use of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints on the detailed modeling of the initial-state condition and the fluctuations of the medium created in heavy-ion collisions and the better constraints on the initial-state conditions will certainly improve the uncertainties of determining $\eta/s(T)$.

The results with the comparison to VISH2+1 calculation~\cite{Zhu:2016puf} are shown in Fig.~\ref{fig:Figure_3}.  All the models with the large share viscosity regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial condition) fails to capture the centrality dependence of SC(3,2) and SC(4,2). 
And among the models with small shear viscosities ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) but they cannot describe the data quantitively for most of the centrality ranges.
As similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalised NSC(3,2) in these models is opposite to the data in 0-10\% central collisions. NSC(3,2) does not show sensitivity to initial conditions or $\eta/s$ parametrizations and cannot be described by these models quantitively.
However, for NSC(4,2), it is sensitive both to initial conditions and $\eta/s$ parametrizations.
Even though NSC(4,2) is favoured both by AMPT initial condition with $\eta/s$=0.08 and MC-Glauber initial condition with $\eta/s=0.20$,
SC(4,2) can be only described by smaller $\eta/s$ from AMPT and MC-Glauber initial conditions. Therefore the Glauber initial condition with $\eta/s=0.20$ model can be ruled out and we come to a conclusion based on the tested model parameters that $\eta/s$ should be small and AMPT initial condition is favoured by the data.

@@

Finally, the extracted results  from particle level AMPT simulations in the same way as for the data are compared to the data in Fig.~\ref{fig:Figure_4}.
As for SC(3,2), neither of the settings can describe the data and the setting with the default AMPT model somewhat follows the trend of the data closest. The same setting can describe NSC(3,2) fairly well and also the sign of NSC(3,2) is well reproduced by this setting while all the hydrodynamic calculations in this article failed to describe the sign of the observable in the most central collisions.
Interestingly the string melting AMPT model cannot capture the data well where the strength of the correlation is weaker than the default model.
The third version based on the string melting configuration with the hadronic rescattering phase off is also shown to quantify its influence.
This late hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but it is not enough to describe the data.
Further we investigated why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2). By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, we were able to recover the difference in SC(3,2) between the data and the model. The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values reported in \cite{Adam:2016nfo} in all the centrality ranges.

In the case of SC(4,2), the string melting AMPT model can fairly well describe the data while the default model underestimates it.
NSC(4,2) is slightly overestimated by the same setting which can describe SC(4,2) but the default AMPT model can describe the data better.
The influence of the hadronic rescattering phase for NSC(4,2) is opposite to other observables (SC(3,2), NSC(3,2) and SC(4,2)), where the hadronic rescattering make NSC(4,2) slightly smaller.
It should be noted that the better agreement for SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between AMPT and data as it was demonstrated for SC(3,2).
Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constraints to the parameters in AMPT models.

@@

\subsection{Higher Order Harmonic Correlations}
The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical calculations. 
First, the fluid hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_5}. 
\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{Niemi:2015qia}, figure will be replaced later, just a place holder]}}

\begin{figure}[htbp]
            \begin{center}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro.eps}}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro_norm.eps}}
              \end{center}
        \caption{Results from SC(m,n) in $\PbPb$ $\snn=2.76$~TeV are compared to hydrodynamic calculations. The dashed lines are hydrodynamic predictions with various $\eta/s(T)$ parametrizations~\cite{Niemi:2015qia}. This will be replaced with new figures once we have the calculations for Harri}
        \label{fig:Figure_5}
\end{figure}

The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to VISH2+1 calculations~\cite{Zhu:2016puf}, shown in Fig.~\ref{fig:Figure_6}. 
All the models with the large share viscosity regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions, and $\eta/s=0.16$ for AMPT) failed to capture the centrality dependence of SC(5,2), SC(5,2) and SC(5,3), more clearly than lower order harmonic correlations (SC(3,2), SC(4,2)).
And among the models with small shear viscosity ($\eta/s=0.08$), the one from the AMPT initial condition describes the data much better than the other initial conditions. 
A quite clear separation between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
NSC(5,2) and SC(5,3) are quite sensitive to both the initial conditions and the $\eta/s$ parametrizations.
As similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the NSC(4,3) in these models is opposite to the data in 0-10\% central collisions. NSC(4,3) shows sensitivity to both initial conditions and $\eta/s$ parametrizations while NSC(3,2) didn't show sensitivity to initial conditions or $\eta/s$ parametrizations.
SC(4,3) data is clearly favored by smaller $\eta/s$ but NSC(4,3) cannot be described by these models quantitively.

@@

The extracted results  from particle level AMPT simulations in the same way as for the data are compared to the data in Fig.~\ref{fig:Figure_7}.
The string melting AMPT model describes SC(5,2) and SC(5,3) well. The same setting describes only NSC(5,3) but it overestimates NSC(5,2). 
However the default AMPT model can describe NSC(5,3) and NSC(5,2) fairly well as similarly as NSC(3,2) and NSC(4,2).
% intersting AMPT String Melting OFF, Rescatering ON < AMPT String Melting ON, Rescatering OFF
In the case of SC(4,3), neither of the settings can describe the data but the default AMPT model follows the data closest. 
The string melting AMPT model fails to describe SC(4,3) and NSC(4,3).
In summary, the default AMPT model describes the normalized SC (NSC$(m,n)$) from lower to higher order harmonic correlation while the string melting AMPT model overestimates NSC(5,2) and 
underestimates (or very weak correlations) NSC(4,3).

@@

It can be seen in Fig.~\ref{fig:Figure_2} that the $p_{\rm T}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence for the centrality range $<$30\% and shows moderate decreasing trend for increasing $p_{\rm T}$ for $>$30\% centrality range.
NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ or the centrality increase. 
In oder to see the trend more clearly, we show NSC($m$,$n$) results as a function of minimum $p_{\rm T}$ cut in Fig.~\ref{fig:Figure_8}.
NSC(3,2) and NSC(4,2) as a function of different minimum $p_{\rm T}$ cut are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_8}.
These observed $p_{\rm T}$ dependence for NSC(3,2) and NSC(4,2) in mid central collisions is seen also in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
The other AMPT configurations except for the default AMPT model give very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitude of the data both for NSC(3,2) and NSC(4,2).
In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for $40-50\%$ where the model underestimates the data and have stronger $p_{\rm T}$ dependence than the data.
As for  NSC(4,2), the same model which describes NSC(3,2) also can reproduce the data well expect for $10-20\%$ and $40-50\%$ centralities where some deviations from the data both for the magnitude and $p_{\rm T}$ dependence are observed.
When the string melting AMPT model is compared to the same model with the hadronic rescattering off, it is observed that the very strong $p_{\rm T}$ dependence as well as the correlation strength get weaker by the hadronic rescattering.
This might imply that the hadronic interaction is the source of this observed $p_{\rm T}$ dependence even though the relative contributions from partonic and hadronic stage in the final state particle should be studied further.
This observed moderate $p_{\rm T}$ dependence in mid central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out predicted in ~\cite{Luzum:2010ad}.
The comparisons to hydrodynamic models can further help to understand the viscous correction to the momentum distribution at hadronic freeze-out~\cite{Teaney:2012ke,Niemi:2015qia}.
\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{} and VISH2+1 calculations~\cite{Zhu:2016puf}]}}

\begin{figure}[htbp]
             \begin{center}
              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32.eps}}
              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42.eps}}
              \end{center}
             \caption{NSC(3,2) (Top) and SC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts are compared to various AMPT models. The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
             \label{fig:Figure_8}
\end{figure}

@@

\section{Summary}
\label{sec:summary}
In summary, we have measured the Symmetric 2-harmonic 4-particle Cumulants (SC), which quantify the relationship between event-by-event fluctuations of two different flow harmonics. The observables are particularly robust against few-particle non-flow correlations and they provide orthogonal information to recently analysed symmetry plane correlators. We have found that fluctuations of $v_2$ and $v_3$ ($v_3$ and $v_4$) are anti-correlated in all centralities and fluctuations of $v_2$ and $v_4$ ( $v_2$ and $v_5$, $v_3$ and $v_5$) are correlated for all centralities. 
This feature was explored to discriminate between various hydro model calculations with different initial conditions as well as different parametrizations of the temperature dependence of $\eta/s$.
We have found that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties. Therefore they have discriminating power on separating the role of the $\eta/s$  from the initial condition to the final state particle anisotropies.
Furthermore, the sign of $v_3$-$v_2$ correlation in the model in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations.
In the most central collisions the anisotropies originate mainly from fluctuations, i.e.\ the initial ellipsoidal geometry characteristic for mid-central collisions plays little role in this regime. Hence this observation might help to understand the details of the fluctuations in initial conditions. 
The comparisons to VISH2+1 calculation show that all the models with the large share viscosity regardless of the initial conditions failed to capture the centrality dependence of higher order correlations, more clearly than lower order harmonic correlations and based on the tested model parameters that the $\eta/s$ should be small and AMPT initial condition is favored by the data. A quite clear separation of the correlation strength between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
Finally we have found that $v_3$-$v_2$ and $v_4$-$v_2$ correlations have moderate $p_{\rm T}$ dependence in mid central collisions. This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out.
The results presented in this article can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties in ultra-relativistic heavy-ion collisions.

>>>>

@@

The correlations between event-by-event fluctuations of amplitudes of anisotropic flow harmonics
in $\PbPb$ collisions at $\snn=2.76$~TeV have been measured with the ALICE detector at the Large Hadron Collider. 
The results were obtained with the new multi-particle cumulant method dubbed symmetric cumulants.
This method is robust against systematic biases originating from non-flow effects. 
The centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations are presented. 
The results are compared to calculations from viscous hydrodynamics and  A Multi-Phase Transport ({AMPT}) models.
The comparisons to viscous hydrodynamic models demonstrate that
the different order Fourier harmonic correlations respond differently to the initial conditions or the shear viscosity to the entropy density ratio ($\eta/s$). The small $\eta/s$ regardless of initial conditions is favored and the small $\eta/s$ with the AMPT initial condition is closest to the results. 
$v_3$-$v_2$ and $v_4$-$v_2$ correlations show moderate $p_{\rm T}$ dependence in mid-central collisions. This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out, which might help to understand bulk viscosity in hadronic phase.
% which is the least understood part of hydrodynamic calculations.
%However the $v_3$-$v_2$ and  $v_4$-$v_3$ cannot be described by any model setting.
%pt dependence ??
Together with the existing measurements of individual flow harmonics the presented results provide further constraints 
on initial conditions and the transport properties of the system produced in heavy-ion collisions.
\end{abstract}
\end{titlepage}
\setcounter{page}{2}

@@

\begin{figure}[htbp]
            \begin{center}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
        \caption{The result of SC($m$,$n$) (left figure) and NSC($m$,$n$) (right figure) with flow harmonic order up to $5^{\mathrm{th}}$ in $\PbPb$ collisions at $\snn=2.76$~TeV. The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from the recent publication~\cite{ALICE:2016kpq} and shown as bands. Note that the systematic and statistical errors are merged quadratically for these lower order harmonic correlations  and SC(4,2) and SC(3,2) on the left figure are scaled down by factor of 10.}
        \label{fig:Figure_1}
              \end{center}
\end{figure}

@@

\section{Model Comparisons}
\label{sec:theory}
\subsection{Low Order Harmonic Correlations}
SC(3,2) and SC(4,2) are compared to several theoretical calculations. 
First, the hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown on the in Fig.~2 in Ref.~\cite{ALICE:2016kpq}. 
It has been demonstrated that NSC(3,2) observable is sensitive mainly to the initial conditions, while NSC(4,2) observable is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
However, the sign of NSC(3,2) is positive in the models in 0-10\% central collisions while it is negative in data.
In the most central collisions the anisotropies originate mainly from fluctuations, i.e.\ the initial ellipsoidal geometry characteristic for mid-central collisions plays little role in this regime. Hence this observation will help to understand the fluctuations in initial conditions better.
NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe neither the centrality dependence nor the absolute values. These observed distinct discrepancy between data and theoretical predictions indicate that the current understanding of initial conditions used to model the initial stages of heavy-ion collision need to be revisited to further constrain the $\eta/s(T)$, considering the difficulties on separating the role of the $\eta/s$  from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
Hence the use of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints on the detailed modeling of the initial state conditions and the fluctuations of the medium created in heavy-ion collisions. The better constraints on the initial state conditions will certainly reduce the uncertainties of determining $\eta/s(T)$.

The results with the comparison to VISH2+1 calculation~\cite{Zhu:2016puf} are shown in Fig.~\ref{fig:Figure_3}.  All the models with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial condition) fail to capture the centrality dependence of SC(3,2) and SC(4,2). 
On the other hand, among the models with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) in general but it cannot describe the data quantitively for most of the centrality ranges.
Similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalised NSC(3,2) in these models is opposite to its signature in the data in 0-10\% central collisions. NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parametrizations and cannot be described by these models quantitively.
However NSC(4,2) is sensitive both to initial conditions and $\eta/s$ parametrizations.
Even though NSC(4,2) favors both AMPT initial condition with $\eta/s=0.08$ and MC-Glauber initial condition with $\eta/s=0.20$,
SC(4,2) can be only described by smaller $\eta/s$ from AMPT and MC-Glauber initial conditions. Because the Glauber initial condition with $\eta/s=0.20$ can be ruled out, we come to a conclusion based on the tested model parameters that $\eta/s$ should be small and AMPT initial condition is favored by the data.

@@

Finally, the extracted results for final state particles from AMPT simulations in the same way as for the data are compared in Fig.~\ref{fig:Figure_4}.
As for SC(3,2), neither of the settings can describe the data and the setting with the default AMPT model somewhat follows the trend of the data closest. The same setting can describe NSC(3,2) fairly well and also the sign of NSC(3,2) is well reproduced by this setting while all the hydrodynamic calculations in this article failed to describe the sign of the observable in the most central collisions.
Interestingly the string melting AMPT model cannot capture the data well where the strength of the correlation is weaker than the default model.
The third version based on the string melting configuration with the hadronic rescattering phase off is also shown to quantify its influence.
This late hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but it is not enough to describe the data.
Further we investigated why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2). By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, we were able to recover the difference in SC(3,2) between the data and the model. The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values reported in \cite{Adam:2016nfo} in all the centrality ranges.

In the case of SC(4,2), the string melting AMPT model can fairly well describe the data while the default model underestimates it.
NSC(4,2) is slightly overestimated by the same setting which can describe SC(4,2) but the default AMPT model can describe the data better.
The influence of the hadronic rescattering phase for NSC(4,2) is opposite to other observables (SC(3,2), NSC(3,2) and SC(4,2)), where the hadronic rescattering makes NSC(4,2) slightly smaller.
It should be noted that the better agreement for SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between AMPT and data as it was demonstrated for SC(3,2).
Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constraints to the parameters in AMPT models.

@@

\subsection{Higher Order Harmonic Correlations}
The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical calculations. 
First, the hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_5}. 
\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{Niemi:2015qia}, figure will be replaced later, just a place holder]}}

\begin{figure}[htbp]
            \begin{center}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro.eps}}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig1_QConly_hydro_norm.eps}}
              \end{center}
        \caption{Results from SC($m$,$n$) in $\PbPb$ at $\snn=2.76$~TeV are compared to hydrodynamic calculations. The dashed lines are hydrodynamic predictions with various $\eta/s(T)$ parametrizations~\cite{Niemi:2015qia}. This will be replaced with new figures once we have the calculations for Harri}
        \label{fig:Figure_5}
\end{figure}

The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to VISH2+1 calculations~\cite{Zhu:2016puf}, shown in Fig.~\ref{fig:Figure_6}. 
All the models with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions, and $\eta/s=0.16$ for AMPT) failed to capture the centrality dependence of SC(5,2), SC(5,2) and SC(5,3), more clearly than for the lower order harmonic correlations (SC(3,2) and SC(4,2)).
Among the models with small $\eta/s$ ($\eta/s=0.08$), the one from the AMPT initial condition describes the data much better than the ones with other initial conditions. 
A quite clear separation between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
NSC(5,2) and SC(5,3) are quite sensitive to both the initial conditions and the $\eta/s$ parametrizations.
Similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the NSC(4,3) in these models is opposite to its signature in the data in 0-10\% central collisions. NSC(4,3) shows sensitivity to both initial conditions and $\eta/s$ parametrizations.
% while NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parametrizations.
SC(4,3) data is clearly favored by smaller $\eta/s$ but NSC(4,3) cannot be described by these models quantitively.

@@

The extracted results for final state particles from AMPT simulations in the same way as for the data are compared in Fig.~\ref{fig:Figure_7}.
The string melting AMPT model describes SC(5,3) and NSC(5,3) well. The same setting overestimates SC(5,2) and NSC(5,2). 
However the default AMPT model can describe NSC(5,3) and NSC(5,2) fairly well as it is the case for NSC(3,2) and NSC(4,2) seen in Fig.~\ref{ig:Figure_4}.
% intersting AMPT String Melting OFF, Rescatering ON < AMPT String Melting ON, Rescatering OFF
In the case of SC(4,3), neither of the settings can describe the data but the default AMPT model follows the data closest. 
The string melting AMPT model fails to describe SC(4,3) and NSC(4,3).
In summary, the default AMPT model describes well the normalized symmetric cumulants (NSC$(m,n)$) from lower to higher order harmonic correlations while the string melting AMPT model overestimates NSC(5,2) and underestimates (or predicts very weak correlation) NSC(4,3).

@@

It can be seen in Fig.~\ref{fig:Figure_2} that the $p_{\rm T}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence for the centrality range $<$30\% and shows moderate decreasing trend for increasing $p_{\rm T}$ for $>$30\% centrality range.
NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ or the centrality increase. 
In oder to see the trend more clearly, we show NSC($m$,$n$) results as a function of minimum $p_{\rm T}$ cut in Fig.~\ref{fig:Figure_8}.
NSC(3,2) and NSC(4,2) as a function of different minimum $p_{\rm T}$ cut are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_8}.
These observed $p_{\rm T}$ dependence for NSC(3,2) and NSC(4,2) in mid-central collisions is seen also in AMPT simulations for higher minimum $p_{\rm T}$ cuts.
The other AMPT configurations except for the default AMPT model give very strong $p_{\rm T}$ dependence above 1~GeV/$c$ and cannot describe the magnitude of the data both for NSC(3,2) and NSC(4,2) simultaneously.
In the case of NSC(3,2), the default AMPT model describes the magnitude and $p_{\rm T}$ dependence well in all collision centralities except for $40-50\%$ where the model underestimates the data and have stronger $p_{\rm T}$ dependence than the data.
As for  NSC(4,2), the same model which describes NSC(3,2) also can reproduce the data well expect for $10-20\%$ and $40-50\%$ centralities where some deviations from the data both for the magnitude and $p_{\rm T}$ dependence are observed.
When the string melting AMPT model is compared to the same model with the hadronic rescattering off, it is observed that the very strong $p_{\rm T}$ dependence as well as the correlation strength get weaker by the hadronic rescattering.
This might imply that the hadronic interaction is the source of this observed $p_{\rm T}$ dependence even though the relative contributions from partonic and hadronic stage in the final state particle should be studied further.
This observed moderate $p_{\rm T}$ dependence in mid-central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out predicted in ~\cite{Luzum:2010ad}.
The comparisons to hydrodynamic models can further help to understand the viscous correction to the momentum distribution at hadronic freeze-out~\cite{Teaney:2012ke,Niemi:2015qia}.
\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{} and VISH2+1 calculations~\cite{Zhu:2016puf}]}}

\begin{figure}[htbp]
             \begin{center}
              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32.eps}}
              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42.eps}}
              \end{center}
             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts are compared to various AMPT models. The details of the AMPT configurations can be found in Sec.~\ref{sec:models}.}
             \label{fig:Figure_8}
\end{figure}

@@

\section{Summary}
\label{sec:summary}
In summary, we have measured the Symmetric 2-harmonic 4-particle Cumulants (SC) to higher order Fourier harmonic (up to $5^{\mathrm{th}}$ order) correlations as well as to $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$). 
We have found that fluctuations of $v_2$ and $v_3$ ($v_3$ and $v_4$) are anti-correlated in all centralities while fluctuations of $v_2$ and $v_4$ ($v_2$ and $v_5$, $v_3$ and $v_5$) are correlated for all centralities. 
This feature was explored to discriminate between various hydro model calculations with different initial conditions as well as different parametrizations of the temperature dependence of $\eta/s$.
We have found that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties. Therefore they have discriminating power on separating the role of the $\eta/s$  from the initial conditions to the final state particle anisotropies.
Furthermore, the sign of $v_3$-$v_2$ correlation in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations.
In the most central collisions the anisotropies originate mainly from fluctuations, i.e.\ the initial ellipsoidal geometry characteristic for mid-central collisions plays little role in this regime. Hence this observation might help to understand the details of the fluctuations in initial conditions. 
The comparisons to VISH2+1 calculation show that all the models with large $\eta/s$ regardless of the initial conditions failed to capture the centrality dependence of higher order correlations, more clearly than lower order harmonic correlations. 
Based on the tested model parameters, the $\eta/s$ should be small and AMPT initial condition is favored by the data. A quite clear separation of the correlation strength between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
Finally, we have found that $v_3$-$v_2$ and $v_4$-$v_2$ correlations have moderate $p_{\rm T}$ dependence in mid-central collisions. This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out.
The results presented in this article can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.
